R Notebook

### 2021-11-20 group-e/group-e-analysis.Rmd
minor updates to CDS abstract fig
minor addition to grp E analysis

@@

>>>>

<!--re-reading the paper, I think the KS test is over fitted parameters? -RR-->

@@

alternative analyses with mixed effects models:
<!--added these when working on CDS abstract -RR-->

```{r}
summary.gaze.view.subject$time.window.c<-scale(summary.gaze.view.subject$time.window, center=T, scale=F )
summary(lmer(prop.in.target.subject ~ task*time.window.c + (1 + time.window.c|subject_id), data = summary.gaze.view.subject))
```

regression with lag predictor

```{r}
summary.gaze.view.subject = summary.gaze.view.subject %>% 
  group_by(subject_id,task) %>% 
  mutate(lag1_prop = lag(prop.in.target.subject))
```

```{r}
summary(lmer(prop.in.target.subject ~ task + lag1_prop + (1 + lag1_prop |subject_id), data = summary.gaze.view.subject))
```
